SI

### 2021-01-05 ms/si.Rmd
Add gametophytes to DT control plot

# Prepare data for plotting
sporo_control_plot_data <-
  # Start with DT data
  filmy_dt %>%
  filter(salt == "Control", generation == "sporophyte") %>%
  # Filter out individuals with low pre-treatment yields
  filter(!is.na(yield_pre), yield_pre > 400) %>%
  # Calculate recovery by individual
  verify(yield_pre > 0) %>%
  assert(not_na, yield_pre) %>%
  select(species, salt, dry_time, individual, dataset, contains("yield")) %>%
  select(-yield_72hr, -contains("yield_dry")) %>%
  pivot_longer(names_to = "rec_time", values_to = "yield_recover", matches("30|24|48")) %>%
  mutate(
    rec_time = str_remove_all(rec_time, "yield_"),
    recovery = yield_recover / yield_pre) %>%
  select(-contains("yield")) %>%
  # Calculate mean recovery by species and dataset
  mutate(rec_time = factor(rec_time, levels = c("30min", "24hr", "48hr"))) %>%
  group_by(species, salt, dry_time, rec_time, dataset) %>%
  summarize(
    recovery_mean = mean(recovery, na.rm = TRUE),
    sd = sd(recovery, na.rm = TRUE),
    n = n(),
    .groups = "drop") %>%
  rename(recovery = recovery_mean) %>%
  # Add growth habit data
  left_join(filmy_habit, by = "species") %>%
  assert(not_na, habit) %>%
  mutate(
    habit = str_replace_all(habit, "_", " ") %>% 
      str_to_sentence() %>%
      factor(levels = c("Terrestrial", "Saxicolous", "Low epiphyte", "High epiphyte"))) %>%
  # Add dataset year
  mutate(year = str_split(dataset, "_") %>% map_chr(1)) %>%
  # Abbreviate species names to "G. species"
  mutate(
    species = str_replace_all(species, "[a-z]+_", ". "),
    species = glue("*{species}*")) %>%
  # Add year to species names with multiple datasets
  add_count(species, name = "n_species") %>%
  mutate(species = ifelse(n_species > 6, paste(species, year), species)) %>%
  select(-n_species) %>%
  # Only keep rows with recovery
  filter(!is.na(recovery))

# Make plot
ggplot(sporo_control_plot_data, aes(x = rec_time, y = recovery, shape = dry_time, fill = salt)) +
  geom_point(position = pd, size = 1.5, fill = "white") +
  geom_errorbar(
    aes(ymin = recovery - sd, ymax = recovery + sd), 
    colour = "grey50", width = 0, 
    position = pd) +
  facet_wrap(vars(habit, species)) +
  scale_shape_manual(name = "Desiccation Time",
                        values = c(24, 21),
                        breaks = c("15", "2"),
                        labels = c("15 days", "2 days")) +
  scale_y_continuous(label = label_percent(accuracy = 1)) +
  scale_x_discrete(limits = c("30min","24hr","48hr"),
                   labels = c("0.5", "24", "48")) +
  xlab("Recovery Time (hr)") +
  ylab("Recovery (%)") +
  theme_bw() +
  legend_theme +
  theme(legend.position ="bottom",
        panel.grid.minor = element_blank(), 
        panel.grid.major.x = element_blank(),
        strip.text = element_markdown()
)
```

**Figure SXX**. Recovery of controls (samples kept on moist tissues) for desiccation tolerance test of filmy fern sporophytes from Moorea, French Polynesia. Recovery was measured by comparing maximum photochemical yield of photosystem II before desiccation treatment with values at 30 min, 24 hr, and 48 hr following desiccation treatment (see Methods). Recovery was not measured for all combinations of species and desiccation treatments; missing points indicate data not collected (not recovery of 0%).

>>>>

# Prepare data for plotting
dt_control_plot_data <-
  # Start with DT data
  filmy_dt %>%
  filter(salt == "Control") %>%
  # Filter out individuals with low pre-treatment yields
  filter(!is.na(yield_pre), yield_pre > 400) %>%
  # Calculate recovery by individual
  verify(yield_pre > 0) %>%
  assert(not_na, yield_pre) %>%
  select(species, salt, dry_time, individual, dataset, generation, contains("yield")) %>%
  select(-yield_72hr, -contains("yield_dry")) %>%
  pivot_longer(names_to = "rec_time", values_to = "yield_recover", matches("30|24|48")) %>%
  mutate(
    rec_time = str_remove_all(rec_time, "yield_"),
    recovery = yield_recover / yield_pre) %>%
  select(-contains("yield")) %>%
  # Calculate mean recovery by species and dataset
  mutate(rec_time = factor(rec_time, levels = c("30min", "24hr", "48hr"))) %>%
  group_by(species, salt, dry_time, rec_time, generation, dataset) %>%
  summarize(
    recovery_mean = mean(recovery, na.rm = TRUE),
    sd = sd(recovery, na.rm = TRUE),
    n = n(),
    .groups = "drop") %>%
  rename(recovery = recovery_mean) %>%
  # Add growth habit data
  left_join(filmy_habit, by = "species") %>%
  assert(not_na, habit) %>%
  mutate(
    habit = str_replace_all(habit, "_", " ") %>% 
      str_to_sentence() %>%
      factor(levels = c("Terrestrial", "Saxicolous", "Low epiphyte", "High epiphyte"))) %>%
  # Add dataset year
  mutate(year = str_split(dataset, "_") %>% map_chr(1)) %>%
  # Abbreviate species names to "G. species"
  mutate(
    species = str_replace_all(species, "[a-z]+_", ". "),
    species = glue("*{species}*")) %>%
  # Add year to species names with multiple datasets
  add_count(species, name = "n_species") %>%
  mutate(species = ifelse(n_species > 6 & generation == "sporophyte", paste(species, year), species)) %>%
  select(-n_species) %>%
  # Only keep rows with recovery
  filter(!is.na(recovery))

# Make plot: sporophyte controls
a <-
  dt_control_plot_data %>% 
  filter(generation == "sporophyte") %>%
  ggplot(aes(x = rec_time, y = recovery, shape = dry_time, fill = salt)) +
  geom_point(position = pd, size = 1.5, fill = "white") +
  geom_errorbar(
    aes(ymin = recovery - sd, ymax = recovery + sd), 
    colour = "grey50", width = 0, 
    position = pd) +
  facet_wrap(vars(habit, species)) +
  scale_shape_manual(name = "Desiccation Time",
                     values = c(24, 21),
                     breaks = c("15", "2"),
                     labels = c("15 days", "2 days")) +
  scale_y_continuous(label = label_percent(accuracy = 1)) +
  scale_x_discrete(limits = c("30min","24hr","48hr"),
                   labels = c("0.5", "24", "48")) +
  xlab("Recovery Time (hr)") +
  ylab("Recovery (%)") +
  theme_bw() +
  legend_theme +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank(), 
    panel.grid.major.x = element_blank(),
    strip.text = element_markdown(),
    axis.title.x = element_blank()
  )

# Make plot: gametophyte controls
b <-
  dt_control_plot_data %>% 
  filter(generation == "gametophyte") %>% 
  ggplot(aes(x = rec_time, y = recovery, shape = dry_time, fill = salt)) +
  geom_point(position = pd, size = 1.5, fill = "white") +
  geom_errorbar(
    aes(ymin = recovery - sd, ymax = recovery + sd), 
    colour = "grey50", width = 0, 
    position = pd) +
  facet_wrap(vars(habit, species)) +
  scale_shape_manual(name = "Desiccation Time",
                        values = c(24, 21),
                        breaks = c("15", "2"),
                        labels = c("15 days", "2 days")) +
  scale_y_continuous(label = label_percent(accuracy = 1)) +
  scale_x_discrete(limits = c("30min","24hr","48hr"),
                   labels = c("0.5", "24", "48")) +
  xlab("Recovery Time (hr)") +
  ylab("Recovery (%)") +
  theme_bw() +
  theme(
        panel.grid.minor = element_blank(), 
        panel.grid.major.x = element_blank(),
        strip.text = element_markdown()
) +
  # Use guides to make the legend go away
  # otherwise it will be duplicated by patchwork
  # https://github.com/thomasp85/patchwork/issues/170#issuecomment-641310103
  guides(shape = "none")

a + b + plot_layout(guides = "collect", ncol = 1, heights = c(85, 15)) + plot_annotation(tag_levels = "a") &
  theme(legend.position='bottom')
```

**Figure SXX**. Recovery of controls (samples kept on moist tissues) for desiccation tolerance test of filmy fern sporophytes (**a**) and gametophytes (**b**) from Moorea, French Polynesia. Recovery was measured by comparing maximum photochemical yield of photosystem II before desiccation treatment with values at 30 min, 24 hr, and 48 hr following desiccation treatment (see Methods). Recovery was not measured for all combinations of species and desiccation treatments; missing points indicate data not collected (not recovery of 0%). Gametophytes only included a single individual per species thus lack error bars.
